\documentclass[margin,line]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{\Large{Kevin M. Purcell} \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
National Marine Fisheries Service  & {\it Voice:}  (337) 296-6294 \\            
Southeast Fishery Science Center   & {\it Fax:}    (412) 268-7828 \\         
Beaufort Laboratory                & {\it E-mail:}  kevin@kevin-purcell.com\\       
Beaufort NC, 28516 USA             & {\it web:} www.kevin-purcell.com \\     
\end{tabular}


\section{\sc Research Interests}
Bayesian statistics, spatial statistics, nonparametric regression,
statistical methods for large datasets, statistics for public policy

\section{\sc Education}
	{\bf University of Louisiana at Lafayette}, Lafayette, LA USA\\
	%{\em Department of Biology} 
	\vspace*{-.1in}
	\begin{list1}
	\item[] Ph.D., Environmental and Evolutionary Biology, 2009

	\vspace*{.05in}

	\end{list1}

	{\bf Bloomsburg University}, Bloomsburg, PA USA\\
	%{\em Department of Mathematics and Statistics} 
	\vspace*{-.1in}
	\begin{list1}
	\item[] M.S., Biology,  2003
	\end{list1}

	{\bf East Stroudsburg University}, East Stroudsburg, PA USA\\
	%{\em Department of Mathematics and Statistics} 
	\vspace*{-.1in}
	\begin{list1}
	\item[] B.S., Biology,  1999
	\item[] B.S., Marine Science,  1999
	\end{list1}

\section{\sc Professional Experience}
	{\bf Duke University \& NOAA Fisheries}, Beaufort, NC USA

	\vspace{-.3cm}
	{\em Postdoctoral Associate} \hfill {\bf 2011 - present}\\
	%\vspace{-.1cm}
	{\em Instructor} \hfill {\bf May - June, 2002}\\
	Co-taught graduate level course for the Master of Science in
	Computational Finance program.  Shared responsibility for lectures, exams,
	homework assignments, and  grades.  
	\vspace*{.05in}  
	\begin{list2}
	\item 46-731 Probability and Statistics, Summer 2002.
	\end{list2}




\section{\sc Publications}
B.J. Langseth, \textbf{K.M. Purcell}, J.K. Craig, A.M. Schueller, J.W. Smith, K. W. Shertzer, S. Creekmore, K.A. Rose, K. Fennel. 2014. Effect of changes in dissolved oxygen concentrations on the spatial dynamics of the Gulf Menhaden fishery in the northern Gulf of Mexico. \textit{Marine and Coastal Fisheries}. (\textit{In review})

\textbf{K. M. Purcell} and C. A. Stockwell. 2013. Mechanism dictating the structure and dispersal of a non-native invasive fish species to New Zealand. \textit{Biological Invasions}. (\textit{In review})

D. Enfield, G. Goni, F. Bringas, D. Lindo, S.-Ki Lee, Y. Liu, B. Muhling, L. Avens, J. Agar, J. Litz, P. Richards, L. Garrison, \textbf{K. M. Purcell}, J. Smith, N. Bartlein, T. Minello, B. McAnally, D. Apeti, H. Perryman. (editors) M. Kamauskas, M. J. Schirripa, C. Kelble, G. Cook, J. K. Craig. 2013. Gulf of Mexico Ecosystem Status Report. \textit{NOAA Technical Memorandum} #NMFS-SEFSC--653.

C. A. Stockwell, J. S. Heilveil, \textbf{K. M. Purcell}. 2012. Estimating divergence time for two evolutionarily significant units of a protected fish species. \textit{Conservation Genetics} 14:215--222.
\textbf{K. M. Purcell}, P. L. Klerks, A. T. Hitch, P. L. Leberg. 2012. The role of genetic structure in the adaptive divergence of populations experiencing saltwater intrusion due to relative sea-level rise. \textit{J. Evolutionary Biology} 25:2623--2632.

\textbf{K. M. Purcell}, N. Ling, C. A. Stockwell. 2012. Evaluation of the introduction history and genetic diversity of a serially introduced fish population in New Zealand. \textit{Biological Invasions} 14:2057--2065.

C. A. Stockwell, \textbf{K. M. Purcell}, M. L. Collyer, J. Janovy. 2011. Translocations alter parasite communities of a protected species due to the environmental tolerance mismatch among hosts. \textit{Transactions of the American Fisheries Society} 140:1370--1374.

\textbf{K. M. Purcell}, S. L. Lance, K. L. Jones, C.A. Stockwell. 2011. Ten novel microsatellite markers for the western Mosquitofish, \textit{Gambusia affinis}. \textit{Conservation Genetic Resources} 3: 361--363.

A. T. Hitch, S. B. Martin, \textbf{K. M. Purcell}, P. L. Klerks, P. L. Leberg. 2010. Interactions of salinity, marsh fragmentation and submerged aquatic vegetation on resident nekton assemblages of coastal marsh ponds. \textit{Estuaries and Coasts} 34: 653--662.

		\item \textbf{K. M. Purcell}, P. L. Klerks, P. L. Leberg. 2010. Adaptation to sea level rise: Does local adaptation influence the demography of coastal fish populations. \textit{Journal of Fish Biology} 77:1209--1218.
    
    S. B. Martin, A. T. Hitch, \textbf{K. M. Purcell}, P. L. Klerks, P. L. Leberg. 2009. Life history variation along a salinity gradient in coastal marshes. \textit{Aquatic Biology} 8:15--28.
    
\textbf{K. M. Purcell}, A. T. Hitch, P. L. Klerks, P. L. Leberg. 2008. Adaptation as a potential response to sea-level rise: a genetic basis for salinity tolerance in populations of a coastal marsh fish. \textit{Evolutionary Applications} 1: 155--€“160.

P. L. Leberg, M. C. Green, B. A. Adams, \textbf{K. M. Purcell}, M. C. Luent. 2007. Response of waterbird colonies in southern Louisiana to recent drought and hurricanes. \textit{Animal Conservation} 10: 502--€“508.

\section{\sc Papers in preparation}

\textbf{K. M. Purcell}, J. Nance, M. Smith, J. K. Craig. 2014. Coastal hypoxia and its effects on the spatial dynamics of a large marine fishery. (44 pgs, 9 fig, 1 table)

\textbf{K. M. Purcell} and J. K. Craig. 2014. Global fishery imports and Eutrophication: synergistic effects on the demersal nekton community of the Gulf of Mexico. (37 pgs, 5 figs, 2 tables)

\section{\sc Conference Presentations}
Paciorek, C.J., J.S. Risbey, V. Ventura, and R.D.Rosen.  2001.  Changes in Northern Hemisphere winter storm activity (1949-1999) based
on a comparison of cyclone indices.  8th International Meeting on
Statistical Climatology, Luneberg, Germany, March, 2001.

Paciorek, C.J. and R. Rosenfeld.  2000.  Minimum classification error
training in exponential language models.  2000 Spring Transcription
Workshop, College Park, Maryland.
\vspace*{-.25in}  
\begin{verbatim}http://www.nist.gov/speech/publications/tw00/html/abstract.htm#cp1-50\end{verbatim}

\section{\sc Professional Experience}
{\bf Bureau of Transportation Statistics, U.S. Department of
  Transportation}, Washington, District of Columbia USA

\vspace{-.3cm}
{\em Summer researcher} \hfill {\bf May, 2000 - August, 2000}\\
Carried out several consulting projects, including modelling of
injuries to cadavers in crash test experiments, analysis of airline
delay data, and advice on analysis of airline economics data.

{\bf Abt Associates}, Bethesda, Maryland USA

\vspace{-.3cm}
{\em Associate Programmer Analyst and Research Assistant} \hfill {\bf
  October, 1994 - August, 1996}\\
Researcher and computer model developer for U.S. EPA Regulatory Impact
Analysis of Section 403 Lead Paint Hazard Rule.  Other projects
included database analysis, literature reviews, and cost-benefit analysis.

\section{\sc Computer Skills} 
\begin{list2}
\item Statistical Packages:  R, S-Plus, BUGS; some experience
  with SAS; extensive use of C and Fortran statistical libraries.
\item Languages:  C++, Perl, Pascal, some use of Unix shell scripts,
  MPI parallel processing library.
\item Applications: Generic Mapping Tools (GMT) - Unix mapping software, \LaTeX, common Windows
  database, spreadsheet, and presentation software
\item Algorithms: Experience programming Markov Chain Monte Carlo
  simulations of Bayesian posterior distributions
\item Operating Systems:  Unix/Linux, Windows.\\ 
\end{list2}



\end{resume}
\end{document}




